---
output: pdf_document
---

## Loading required packages: knitr
```{r}
require(knitr)
```

```{r}
require(ggplot2)
```
## Loading required packages: ggplot2

```{r}
opts_chunk$set(echo = TRUE)
set.seed(1)
```

n <- 40
lambda <- 0.2
numsim <- 2000

```{r}
dataset <- matrix(rexp(n*numsim, lambda), numsim)
```

```{r}
Theory_Mean <- 1/lambda
Row_Mean <- apply(dataset, 1, mean)
Actual_Mean <- mean(Row_Mean)
Theory_Standard_Deviation <- ((1/lambda)*(1/sqrt(n)))
Actual_Standard_Deviation <- sd(Row_Mean)
Theory_Variance <- Theory_Standard_Deviation^2
Actual_Variance <- var(Row_Mean)
```

# Theoretical Mean = 5.0, Actual Mean = 5.019, Theoritical Standard Deviation = 0.791, Actual Standard Deviation = 0.779, Theoritical Variance = 0.625, Actual Variance = 0.607


dfRow_Mean <- data.frame(Row_Mean) # Convert to data.frame from ggplot

mp <- ggplot(dfRow_Mean, aes(x = Row_Mean))
mp <- mp + geom_histogram(binwidth = lambda, fill = "Red", color = "Blue", aes(y = ..density..))
mp <- mp + labs(title = "Exponential Distribution Density of 40 Numbers", x = "Mean of 40 Selections", y = "Density")
mp <- mp + geom_vline(xintercept = Actual_Mean, size = 1.0, color = "Blue") # add a line for the actual mean
mp <- mp + stat_function(fun = dnorm, args = list(mean = Actual_Mean, sd = Actual_Standard_Deviation), color = "Yellow", size = 1.0)
mp <- mp + geom_vline(xintercept = Theory_Mean, size = 1.0, color = "RED", linetype = "longdash")
mp <- mp + stat_function(fun = dnorm, args = list(mean = Theory_Mean, sd = Theory_Standard_Deviation), color = "Green", size = 1.0)
mp  

